---
title: "p8105_hw5_rw2844"
author: "Renjie Wei"
date: "11/12/2020"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(viridis)
library(plotly)
library(patchwork)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "100%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
set.seed(1)
```


## Problem 1

Read in the data.

```{r homicide_read}
homicide_df = 
  read_csv("homicide-data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa, AL")
```

Summarize the total number of unsolved cases in each of the cities.

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Do a prop test for Baltimore, MD.

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore, MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore, MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Run prop.test for each of the cities in the dataset.

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  # extract both the proportion of unsolved homicides and the confidence interval for each
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

Create a plot that shows the estimates and CIs for each city.

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```


## Problem 2

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time

```{r, lda_data}
lda_df = 
  tibble(
    file = list.files("lda_data"),
  ) %>% 
  mutate(
    path = str_c("lda_data/", file),
    # read in data now
    data = map(path, read_csv)
    ) %>% 
  unnest(data) %>% 
  # extract the group and id
  mutate(
    label = str_extract(file, "(exp_[0-9][0-9]|con_[0-9][0-9])"),
  ) %>% 
  separate(
    label,
    into = c("arm","id"),
    sep = "_"
  ) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "observations",
    names_prefix = "week_"
  ) %>% 
  mutate(
    arm = as.factor(arm),
    id = as.numeric(id),
    week = as.numeric(week),
    observations = as.numeric(observations)
  ) %>% 
  select(-file,-path)

lda_df %>%
  head(10) %>% 
  knitr::kable()
```


```{r spaghetti_plot}
lda_plt1 =
  lda_df %>%
  #create unique id for each participants
  mutate(
    patient_id = str_c(arm, id, sep = "_")
  ) %>% 
  ggplot(
    aes(x = week,
        y = observations,
        color = patient_id
        )
  ) +
  geom_path(aes(group = arm)) +
  ggtitle("A spaghetti chart of the observations on each subject over time")


lda_plt2 =
  lda_df %>%
  mutate(
    patient_id = str_c(arm,id)
  ) %>% 
  ggplot(
    aes(x = week,
        y = observations,
        color = arm
        )
  ) +
  geom_smooth(aes(group = arm), se = F) +
  ggtitle("A regression chart of the observations between control arm and experimental arm")


lda_plt1+lda_plt2

```

To make the trend in different arms clearly, I made a separate regression plot between two arms. And from the regression plot, we can see that the observation value in the control arm stay at the same level, in the contrast, the observation value in the experimental arm increases over time.


## Problem 3

When designing an experiment or analysis, a common question is whether it is likely that a true effect will be detected – put differently, whether a false null hypothesis will be rejected. The probability that a false null hypothesis is rejected is referred to as power, and it depends on several factors, including: the sample size; the effect size; and the error variance. In this problem, you will conduct a simulation to explore power in a simple linear regression.

First set the following design elements:

Fix n=30
Fix σ=5
Set μ=0. Generate 5000 datasets from the model
```{r creat_datasets}
sim_norm = function(n, mu = 0, sigma = 5){
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma),
  )
}

datasets = 
  rerun(5000,sim_norm(30,0,5))
```

x∼Normal[μ,σ]

For each dataset, save μ^ and the p-value arising from a test of H:μ=0 using α=0.05. Hint: to obtain the estimate and p-value, use broom::tidy to clean the output of t.test.

Repeat the above for μ={1,2,3,4,5,6}, and complete the following:

Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power.
Make a plot showing the average estimate of μ^ on the y axis and the true value of μ on the x axis. Make a second plot (or overlay on the first) the average estimate of μ^ only in samples for which the null was rejected on the y axis and the true value of μ on the x axis. Is the sample average of μ^ across tests for which the null is rejected approximately equal to the true value of μ? Why or why not?

